State of the Practice for Lattice Boltzmann Method Software

### 2022-04-01 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Updates to SOP for LBM noticed while working on SOP for MI
Updates to SOP for LBM

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, less common, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Less common artifacts were found in 8 to 15 (30-63\%)
of the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages.  In this section we answer \rqref{RQ_CompareArtifacts} by
comparing the artifacts that we observed in LBM repositories to those observed
and recommended for research software in general. Our comparison may point out
areas where some LBM software packages fall short of current best practices.
This is not intended to be a criticism of any existing packages, especially
since in practice not every project needs to achieve the highest possible
quality.  However, rather than delve into the nuances of which software can
justify compromising which practices we will write our comparison under the
ideal assumption that every project has sufficient resources to match best
practices.

\begin{table}[ht!]
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Installation Guide / Instructions & Design Documentation & Developer / Contributor Manual\\
Issue Tracker & Functional Spec. / Notes & FAQ / Forum\\
Library Dependency List & Performance Information & Requirements Spec.\\
License & Test Plan / Script / Cases & Verification and
Validation Plan\\
List of Related Publications & User Manual / Guide & Video Guide
(including YouTube)\\
Makefile / Build File &  & \\
README File & & \\
Theory Notes & & \\
Tutorial & & \\
Version Control & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency (Sorted Alphabetically)}
\label{artifactspresent}
\end{center}
\end{table}

The top four packages, ESPREsSo, Ludwig, Palabos, and OpenLB, have all of the
common artifacts, except Palabos does not have theory notes and only three
(ESPREsSo, Ludwig, Palabos) of the packages appear to use a version control
system.  The top four packages also have most of the less common artifacts. At
the time of data collection, only one of the four packages (Palabos) did not
have a user manual or guide, but there was a broken link on the package website
indicating that such an artifact might exist. This broken link was later fixed,
but this is not reflected in our data because it was not present at the time of
data collection (mid 2020). Despite the broken link, Palabos does have a
detailed and informative website. As far as we could observe, Ludwig does not
appear to have a publicly visible design and OpenLB does not appear to use a
version control system. However, OpenLB's use of version numbers suggests that
version control may be used privately by the developers.

>>>>

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, uncommon, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Uncommon artifacts were found in 8 to 15 (30-63\%) of
the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages.  We answer \rqref{RQ_CompareArtifacts} by comparing the
artifacts that we observed in LBM repositories to those observed and recommended
for research software in general. Our comparison may point out areas where some
LBM software packages fall short of current best practices. This is not intended
to be a criticism of any existing packages, especially since in practice not
every project needs to achieve the highest possible quality.  However, rather
than delve into the nuances of which software can justify compromising which
practices we will write our comparison under the ideal assumption that every
project has sufficient resources to match best practices.

\begin{table}[ht!]
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Uncommon} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Installation Guide / Instructions & Design Documentation & Developer / Contributor Manual\\
Issue Tracker & Functional Spec. / Notes & FAQ / Forum\\
Library Dependency List & Performance Information & Requirements Spec.\\
License & Test Plan / Script / Cases & Verification and
Validation Plan\\
List of Related Publications & User Manual / Guide & Video Guide
(including YouTube)\\
Makefile / Build File &  & \\
README File & & \\
Theory Notes & & \\
Tutorial & & \\
Version Control & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency (Sorted Alphabetically)}
\label{artifactspresent}
\end{center}
\end{table}

The top four packages, ESPREsSo, Ludwig, Palabos, and OpenLB, have all of the
common artifacts, except Palabos does not have theory notes and only three
(ESPREsSo, Ludwig, Palabos) of the packages appear to use a version control
system.  The top four packages also have most of the uncommon artifacts. At
the time of data collection, only one of the four packages (Palabos) did not
have a user manual or guide, but there was a broken link on the package website
indicating that such an artifact might exist. This broken link was later fixed,
but this is not reflected in our data because it was not present at the time of
data collection (mid 2020). Despite the broken link, Palabos does have a
detailed and informative website. As far as we could observe, Ludwig does not
appear to have a publicly visible design and OpenLB does not appear to use a
version control system. However, OpenLB's use of version numbers suggests that
version control may be used privately by the developers.
